Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2020-10-26 paper/main.tex
add title
intro

\title{Mallows, Black-box combinatorial optimization, limited budget,  ???}
% Double-blind
\author{Double-blind}
% \author{Ekhiñe Irurozki\inst{1} \and Manuel López-Ibáñez\inst{2}\orcidID{0000-0001-9974-1295}}
% \institute{
%    Basque Center for Applied Mathematics\\
%    \email{eirurozki@bcamath.org}
%    \and
%    University of Málaga, Málaga, Spain\\
%    \email{manuel.lopez-ibanez@uma.es}
% }
\date{}%

@@

In this work, we propose and analyze Unbalanced Mallows Model (UMM), a
population-based probabilistic algorithm specifically designed for black-box
combinatorial optimization under a limited budget. There exists a wide body of
research on probabilistic algorithms~\citep{???},\MANUEL{what can we cite from
  that body of research?} with the most prominent examples being estimation of
distribution algorithms (EDAs)~\citep{???}.\MANUEL{what would be the best work
  to cite about EDAs for combinatorial optimization?} ACO may also be
considered a type of EDA, since it builds a probability distribution model from
which solutions are sampled with a bias towards the best solutions evaluated so
far. The proposed UMM drastically differs from EDAs since EDAs assume that
function evaluations are cheap and they can do many of them. On the contrary,
UMM aims at learning as much as possible with a limited number of function
evaluations. Moreover, unlike EDAs, UMM does not rely on a fixed-size
population of solutions that evolves over ``generations''. Instead, taking
inspiration from Bayesian optimizers, UMM considers a sample of permutations
during the whole execution that is increased iteratively by one new permutation
each iteration. Finally, the balance between intensification and exploration is
dynamically adapted by controlling the variance of the probabilistic Mallows model.
\manuel{}{
  \begin{itemize}
  \item Who else has used Mallows model for black-box optimization?
  \item Who else has used unbalanced borda for optimization?
  \end{itemize}
}

>>>>

\title{Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems}
% Double-blind
\author{Double-blind}
% \author{Ekhiñe Irurozki\inst{1} \and Manuel López-Ibáñez\inst{2}\orcidID{0000-0001-9974-1295}}
% \institute{
%    Basque Center for Applied Mathematics\\
%    \email{eirurozki@bcamath.org}
%    \and
%    University of Málaga, Málaga, Spain\\
%    \email{manuel.lopez-ibanez@uma.es}
% }
\date{}%

@@

In this work, we propose and analyze Unbalanced Mallows Model (UMM), a
population-based probabilistic algorithm specifically designed for optimizing
black-box problems over a permutation landscape under a limited budget. There
exists a wide body of research on probabilistic
algorithms~\citep{???},\MANUEL{what can we cite from that body of research?}
with the most prominent examples being estimation of distribution algorithms
(EDAs)~\citep{???}.\MANUEL{what would be the best work to cite about EDAs for
  combinatorial optimization?} ACO may also be considered a type of EDA, since
it builds a probability distribution model from which solutions are sampled
with a bias towards the best solutions evaluated so far. The proposed UMM
drastically differs from EDAs since EDAs assume that function evaluations are
cheap and they can do many of them. On the contrary, UMM aims at learning as
much as possible with a limited number of function evaluations. Moreover,
unlike EDAs, UMM does not rely on a fixed-size population of solutions that
evolves over ``generations''. Instead, taking inspiration from Bayesian
optimizers, UMM considers a sample of permutations during the whole execution
that is increased by one new permutation at each iteration. Finally,
the balance between intensification and exploration is dynamically adapted by
controlling the variance of the probabilistic Mallows model.  \manuel{}{
  \begin{itemize}
  \item Who else has used Mallows model for black-box optimization?
  \item Who else has used unbalanced borda for optimization?
  \end{itemize}
}
